### 2024-09-14 Response/Response.tex

As WDs may require different amounts of power, the problem for each subtask may find different values for $p^u$. Thus, we define $p_{v_d^u}$ as the required ET's power for subtask $v_d^u\in\mathcal{V}_d$. Let $p_{v_d^u}^{\ast}$ and $p^{u^\ast}$ denote the optimal values of $p_{v_d^u}$ and $p^u$, respectively. We know that $p^u$ must be enough to power all WDs. As a result, we can calculate $p^{u^\ast}$ by selecting the maximum $p_{v_d^u}^{\ast}$ as follows.
\begin{equation}\label{eq29}
	p^{u^\ast} = \max_{d\in\mathcal{D}^u}p_{v_d^u}^{\ast},\quad\forall u\in\mathcal{U}.
\end{equation}

In the following remark, we will present an equality constraint for calculating $p_{v_d^u}^{\ast}$.

\begin{remark}
	The following constraint is equivalent to (\ref{eq8}) when $\tau_0^u$ is given.
	\begin{equation}\label{eq30}
		e_1\left(\tau_{1,v_d^u}\right) + e_2\left(\tau_{2,v_d^u}\right) - p_{v_d^u}\tau_0^u = 0.
	\end{equation}
\end{remark}

Based on the definition of $p_{v_d^u}$, $p_{v_d^u}\tau_0^u$ will be the energy required by each subtask $v_d^u\in\mathcal{V}_d$. We know that $e_1\left(\tau_{1,v_d^u}\right) + e_2\left(\tau_{2,v_d^u}\right)$ is the total energy consumption for local computation or offloading of subtask $v_d^u\in\mathcal{V}_d$. In the optimal point of ETEM problem, there should not be any excessive WET. As a result, equality (\ref{eq30}) holds.

We now utilize (\ref{eq28}) and (\ref{eq20})--(\ref{eq30}) to reformulate the ETEM problem into a simplified ETEM problem (S-ETEM) with given offloading decisions $x^{\text{L}}_{v_d^u}$, $x^{\text{M}}_{v_d^u}$, and $x^{\text{C}}_{v_d^u}$.
\begin{subequations}
	\begin{alignat}{4}
		\text{S-ETEM: }\displaystyle{\minimize_{\boldsymbol{p}^\text{v}, \boldsymbol{\tau}_{1}, \boldsymbol{\tau}_{2}}} \quad & \sum_{u\in\mathcal{U}} \sum_{d\in\mathcal{D}^u} e_1\left(\tau_{1,v_d^u}\right)+e_2\left(\tau_{2,v_d^u}\right) \label{eq26}\\
		\textrm{subject to} \quad & 0 \leq p_{v_d^u} \leq P^{\text{ET}, \max}, \forall d\in\mathcal{D}^u, \forall u\in\mathcal{U},\\
		& \text{constraints }(\ref{eq10}), (\ref{eq13}),\\
		%
		\begin{split}
			& \text{constraints }(\ref{eq28}), (\ref{eq30}),\\ & \quad\forall d\in\mathcal{D}^u, \forall u\in\mathcal{U}.
		\end{split}
	\end{alignat}
\end{subequations}
where $\boldsymbol{p}^{\text{v}} \triangleq (p_{v_d^u})_{\sum_{d\in\mathcal{D}}V_d}$, $\boldsymbol{\tau}_{1} \triangleq (\tau_{1,v_d^u})_{\sum_{d\in\mathcal{D}}V_d}$, and $\boldsymbol{\tau}_{2} \triangleq (\tau_{2,v_d^u})_{\sum_{d\in\mathcal{D}}V_d}$.

The above problem is a convex optimization problem. The proof is similar to the proof of Theorem 1 and is omitted due to space limit. \textcolor{blue}{It is also worth noting that for a given $\beta_{v_d^u}$, by solving S-ETEM, we can achieve the optimal solution of the ETEM problem. In other words, by determining the optimal value of $\beta_{v_d^u}$ for each $d\in\mathcal{D}^u$ and $u\in\mathcal{U}$, the optimal ET's transmitted energy can be obtained and there would not be any approximation.}

The S-ETEM problem can be further decomposed as its objective function is separable. Thus, we can have problems specific to each subtask $v_d^u\in\mathcal{V}_d$. We regard these problems as decomposed S-ETEM (DS-ETEM). We can then calculate the weight of each matching as the solution of DS-ETEM which will be individually solved for each subtask $v_d^u\in\mathcal{V}_d$ of WD $d\in\mathcal{D}^u$ and episode $u\in\mathcal{U}$.
\begin{subequations}
	\begin{alignat}{4}
		\text{DS-ETEM: }\displaystyle{\minimize_{p_{v_d^u}, \tau_{1,v_d^u}, \tau_{2,v_d^u}}}\quad &e_1\left(\tau_{1,v_d^u}\right) + e_2\left(\tau_{2,v_d^u}\right) \label{eq31}\\
		%
		\textrm{subject to} \quad&
		\tau^{\min}_{1,v_d^u} \leq \tau_{1,v_d^u} \leq \tau^{\max}_{1,v_d^u},\\
		%
		& \tau^{\min}_{2,v_d^u} \leq \tau_{2,v_d^u} \leq \Gamma^u,\\
		%
		& 0 \leq p_{v_d^u} \leq P^{\text{ET}, \max},\\
		%
		& \text{constraints } (\ref{eq28}), (\ref{eq30}).
	\end{alignat}
\end{subequations}

We continue by presenting \textit{matching rules} \cite{b16} which are constraints on selecting optimal matching to ensure it is a feasible solution of ETEM problem. The first matching rule is that each WD can only be matched to one of the resources corresponding to the equality constraint (\ref{p1c}) in the ETEM problem. Note that each resource can be assigned to multiple WDs. Therefore, we call this matching as a \textit{many-to-one} matching. 
For a specific matching, if the constraints of DS-ETEM problem are satisfied for all subtasks, the matching (i.e., a subset of edges in the matching graph) is considered as a feasible matching \cite{b16}. We exclude the edges corresponding to infeasible matchings from the problem by setting their weights to infinity. Thus, these edges will never be selected in the minimum weight matching as they have infinite edge weights.

Since solving many-to-one matching problems are difficult \cite{b16}, we further convert this matching into a \textit{one-to-one} matching similar to Fig. \ref{fig:4b}. In order to perform this transformation, we first introduce the concept of \textit{virtual resource} as inspired by \cite{b16}. Each virtual resource corresponds to an identical copy of a resource associated to each subtask. The matching between a subtask and a virtual resource is called a \textit{virtual matching}. From Fig. \ref{fig:4a}, it can be observed that subtasks $v_2^1$, $v_3^1$, and $v_3^2$ of WD2 and WD3 are connected to resource $r_2$. We replace this resource with three virtual resources $r_{2,1}$, $r_{2,2}$, and $r_{2,3}$. This makes the many-to-one matching of Fig. \ref{fig:4a}, an equivalent one-to-one matching.

In the next subsection, we propose an algorithm to solve this one-to-one matching.

\subsection{Proposed Algorithm}
In this subsection, we describe our parallel algorithm named WiEnTM to solve the non-convex ETEM problem using the aforementioned minimum weighted graph matching. The algorithm consists of three stages. In the first stage, the weight of all possible matchings are calculated in parallel. We regard this stage as \textit{matching graph weight calculation} (MGW) algorithm. \textcolor{blue}{Note that in order to calculate the weights of subtasks, there is no need to actually execute them. The only required information is the size of input and output of each subtask which is already known from the task call graph. Thus, Lines 4 to 17 of the MGW algorithm can be run simultaneously.} The next stage is intended to find the optimal matchings based on these weights. In the final stage, the algorithm utilizes the optimal virtual matching to determine the desired optimal offloading decisions and scheduling.

Let $\mathcal{R}^{\text{virt}}$ denote the set of virtual resources. We consider $r_{t,v_d^u}^{\text{virt}}\in\mathcal{R}^{\text{virt}}$ as the virtual resource for tier $t\in\{1,2,3\}$ and subtask $v_d^u\in\mathcal{V}_d$. We then define the matrix $\boldsymbol{W}^{\text{virt}} = \left(w_{v_d^u,r_{t,v_d^u}}^{\text{virt}}\right)_{\left(\sum_{d\in\mathcal{D}}{\left(V_d-2\right)}\right)\times|\mathcal{R}^{\text{virt}}|}$ whose entries are the edge weights of the one-to-one matching graph initialized with infinity for all elements. We similarly define matrices $\boldsymbol{T}_i^{\text{virt}} = \left(\tau_{i,v_d^u}^{\text{virt}}\right)_{\left(\sum_{d\in\mathcal{D}}{\left(V_d-2\right)}\right)\times|\mathcal{R}^{\text{virt}}|}, i\in\{1,2,3\}$ and $\boldsymbol{P}^{\text{virt}} = \left(p_{v_d^u}^{\text{virt}}\right)_{\left(\sum_{d\in\mathcal{D}}{\left(V_d-2\right)}\right)\times|\mathcal{R}^{\text{virt}}|}$as auxiliary matrices to store the optimal scheduling times and required powers for different matchings, respectively. As the first and last subtasks are always performed locally, we exclude them from the matching algorithm. Thus, these matrices as well as the power vector will all have $\sum_{d\in\mathcal{D}}{\left(V_d-2\right)}$ rows which corresponds to all subtasks except the first and last ones.
\begin{algorithm}[t]
	\DontPrintSemicolon
	\SetAlgoLined
	\caption{MGW algorithm}\label{alg1}
	\KwIn{$\mathcal{D}, \mathcal{D}^u, \mathcal{R}^{\text{virt}}, \mathcal{V}_d, \mathcal{U}, \Gamma^u, V_d, \tau_{1,v_d^u}^{\min}, \tau_{2,v_d^u}^{\min}, \tau_{3,v_d^u}^{\min}, B_d, \sigma,$ $ \mu_{v_d^u}, g_d, \eta_d, h_d, \beta_{v_d^u}, \tau_0^u, F^{\text{L},\max}_{d}, F^{\text{M},\max}, \forall r_{t,v_d^u}^{\text{virt}}\in\mathcal{R}^{\text{virt}}, t\in\{1,2,3\}, v_d^u\in\mathcal{V}_d, d\in\mathcal{D}, u\in\mathcal{U}$}
	\KwOut{Virtual matching graph weights $\boldsymbol{W}^{\text{virt}}$, virtual scheduling times $\boldsymbol{T}_{1}^{\text{virt}}$, $\boldsymbol{T}_{2}^{\text{virt}}$, $\boldsymbol{T}_{3}^{\text{virt}}$, and virtual power values $\boldsymbol{P}^{\text{virt}}$}

	\SetKwProg{Coblock}{cobegin}{ }{coend}
	$\boldsymbol{W}^{\text{virt}}$ $\leftarrow \left(+\infty\right)_{\left(\sum_{d\in\mathcal{D}}\left(V_d-2\right)\right)\times |\mathcal{R}^{\text{virt}}|}$;\;
	$\boldsymbol{T}_1^{\text{virt}}$, $\boldsymbol{T}_2^{\text{virt}}$, $\boldsymbol{T}_3^{\text{virt}}$ $\leftarrow \left(+\infty\right)_{\left(\sum_{d\in\mathcal{D}}\left(V_d-2\right)\right)\times |\mathcal{R}^{\text{virt}}|}$;\;
	$\boldsymbol{P} ^{\text{virt}}$ $\leftarrow \left(+\infty\right)_{\left(\sum_{d\in\mathcal{D}}\left(V_d-2\right)\right)\times |\mathcal{R}^{\text{virt}}|}$;\;

	\Coblock{$r_{t,v_d^u}\left(0:|\mathcal{R}^{\text{virt}}|\right)$}{
		Assign $x^{\text{L}}_{v_d^u}$, $x^{\text{M}}_{v_d^u}$, and $x^{\text{C}}_{v_d^u}$ based on $r_{t,v_d^u}^{\text{virt}}$;\;

		\tcc{Eqs. (\ref{eq18}), (\ref{eq20}), and (\ref{eq21})}
		\If {$\tau_{j,v_d^u}^{\min} \leq \tau_{j,v_d^u}^{\max}, j\in\{1,2\}$}{
			\eIf{$u\not\in\{0, V_d-1\}$}{
				$\tau_{3,v_d^u}^{\text{virt}^{\ast}} \leftarrow \tau_{3,v_d^u}^{\ast}$; \tcp*{Eq. (\ref{eq18})}
				Solve DS-ETEM for $p_{v_d^u}^{\ast}, \tau_{1,v_d^u}^{\ast}, \tau_{2,v_d^u}^{\ast}$ and assign to $p_{v_d^u}^{\text{virt}^{\ast}} , \tau_{1,v_d^u}^{\text{virt}^{\ast}} , \tau_{2,v_d^u}^{\text{virt}^{\ast}}$;\;
				$w_{v_d^u,r_{t,v_d^u}}^{\text{virt}} \leftarrow e_1\left(\tau_{1,v_d^u}^{\ast}\right) + e_2\left(\tau_{2,v_d^u}^{\ast}\right)$;\;
			}{
				$x^{\text{L}^{\ast}}_{v_d^u} \leftarrow 1$; $x^{\text{M}^{\ast}}_{v_d^u}, x^{\text{C}^{\ast}}_{v_d^u} \leftarrow 0$;\;
				$\tau_{1,v_d^u}^{\ast}, \tau_{3,v_d^u}^{\ast} \leftarrow 0$;\;
				Solve DS-ETEM for $p_{v_d^u}^{\ast}, \tau_{2,v_d^u}^{\ast}$ given $x^{\text{L}^{\ast}}_{v_d^u}, x^{\text{M}^{\ast}}_{v_d^u},x^{\text{C}^{\ast}}_{v_d^u}$;\;
			}
		}
	}
	\Coblock{$v_d^u\left(0:\sum_{d\in\mathcal{D}}\left(V_d-2\right)\right)$}{
		\If {$w_{v_d^u,r_{t,v_d^u}}^{\text{virt}} = +\infty, \forall r_{t,v_d^u}^{\text{virt}}\in\mathcal{R}^{\text{virt}}$}{
			\Return infeasible;
		}
	}
\end{algorithm}

\begin{algorithm}[t]
	\DontPrintSemicolon
	\SetAlgoLined
	\caption{WiEnTM algorithm}\label{alg2}
	\KwIn{$\mathcal{D}, \mathcal{D}^u, \mathcal{R}^{\text{virt}}, \mathcal{V}_d, \mathcal{U}, \Gamma^u, V_d, \tau_{1,v_d^u}^{\min}, \tau_{2,v_d^u}^{\min}, \tau_{3,v_d^u}^{\min}, B_d, \sigma,$ $ \mu_{v_d^u}, g_d, \eta_d, h_d, \beta_{v_d^u}, \tau_0^u, F^{\text{L},\max}_{d}, F^{\text{M},\max}, \forall r_{t,v_d^u}^{\text{virt}}\in\mathcal{R}^{\text{virt}}, t\in\{1,2,3\}, v_d^u\in\mathcal{V}_d, d\in\mathcal{D}, u\in\mathcal{U}$}
	\KwOut{Offloading decisions \mbox{\boldmath$X$}$^{\ast}$, WET powers $\boldsymbol{p}^{\ast}$, and scheduling times $\boldsymbol{T}^{\ast}$}

	\SetKwProg{Coblock}{cobegin}{ }{coend}

	\mbox{\boldmath$X$}$^{\text{virt}^{\ast}} \leftarrow \left(0\right)_{\left(\sum_{d\in\mathcal{D}}\left(V_d-2\right)\right)\times |\mathcal{R}^{\text{virt}}|}$;\;

	Run \textrm{MGW} algorithm;\;

	\Coblock{$v_d^u\left(0:\sum_{d\in\mathcal{D}}\left(V_d-2\right)\right)$}{
		$r_{\min} \leftarrow \textrm{argmin}_{r_{t,v_d^u}\in\mathcal{R}^{\text{virt}}} \left(w_{v_d^u,r_{t,v_d^u}}\right)$;\;
		$x_{v_d^u,r_{\min}}^{\text{virt}^{\ast}} \leftarrow 1$;\;
	}

	\For{$u\in\mathcal{U}$}{
		\Coblock{$d\left(0:|\mathcal{D}^u|\right)$}{
			\If{$u\not\in\{0,V_d-1\}$}{
				Find the non-zero element in \mbox{\boldmath$x$}$^{\text{virt}^{\ast}}_{v_d^u}$ row;\;
				Set $x^{\text{L}^{\ast}}_{v_d^u}, x^{\text{M}^{\ast}}_{v_d^u}, x^{\text{C}^{\ast}}_{v_d^u},$ and $p_{v_d^u}^{\ast}, \tau_{1,v_d^u}^{\ast}, \tau_{2,v_d^u}^{\ast},\tau_{3,v_d^u}^{\ast}$ based on the value of tier number $t$ determined in Line 10 and the outputs of MGW in Line 2;\;
			}
		}
		$p^{u^{\ast}} \leftarrow \max_{d\in\mathcal{D}^u} p_{v_d^u}^{\ast}$;\;
	}
\end{algorithm}

### 2024-09-14 Response/Response.tex

We now explain the MGW algorithm. The first stage of this algorithm (Lines 5-19) requires $|\mathcal{R}^{\text{virt}}|\times \left(\sum_{d\in\mathcal{D}}\left(V_d-2\right)\right)$ parallel executions as shown by a block inside \textit{cobegin} and \textit{coend} keywords. We regard this block as a \textit{kernel}. Each kernel has two input parameters $\lambda_{\text{id}}$ and $\lambda_{\text{count}}$ in the form of $\lambda_\text{id}(0:\lambda_{\text{count}})$ where $\lambda_{\text{id}}$ is the identifier of each kernel and is given during the execution. In addition, $\lambda_{\text{count}}$ is the total number of required executions of the parallel block. In each kernel, the algorithm solves DS-ETEM for virtual resource $r_{t,v_d^u}^{\text{virt}}\in\mathcal{R}^{\text{virt}}$ of subtask $v_d^u\in\mathcal{V}_d$ (Lines 11 and 16) using the techniques such as sequential quadratic programming \cite{b31}. Note that this is a convex problem with only three variables. For the subtasks at both ends, the algorithm enforces the local computation by setting $x^{\text{L}^{\ast}}_{v_d^u} = 1$ and $x^{\text{M}^{\ast}}_{v_d^u} = x^{\text{C}^{\ast}}_{v_d^u} = 0$ (Lines 14-15). It then similarly solves DS-ETEM to obtain optimal values of $\tau_{0,v_d^u}$ and $\tau_{2,v_d^u}$ denoted by $\tau_{0,v_d^u}^{\ast}$ and $\tau_{2,v_d^u}^{\ast}$ (Line 16). Moreover, if $\tau_{j,v_d^u}^{\min} > \tau_{j,v_d^u}^{\max}$ for $j\in\{1,2\}$, the algorithm skips solving DS-ETEM. The next kernel (Lines 20-25) checks for matching feasibility. In the case of having infinite weights for all virtual resources of subtask $v_d^u\in\mathcal{V}_d$, the algorithm stops the executions and indicates the infeasibility. Therefore, checking this condition for each subtask requires $\sum_{d\in\mathcal{D}}\left(V_d-2\right)$ parallel execution.

Next, we analyze the complexity of the MGW algorithm. Problem DS-ETEM is formulated for each subtask $v_d^u\in\mathcal{V}_d$. Thus, it has a time complexity of $O(1)$. The if-statement in the last kernel can also be executed with the time complexity of $O(1)$. This is due to having only three resource options for a given subtask. In order to analyze the time complexity of the parallel algorithm, a parameter known as \textit{depth}\cite{b23} is defined as the time complexity of the longest series of computations that are required to be executed sequentially. Another parameter known as \textit{work}\cite{b23} denotes the total number of primitive works executed by the parallel processor. Therefore, the first kernel of the MGW algorithm has the depth of $O(1)$ and work of $O(UD)$ where $U$ and $D$ are the number of episodes and WDs, respectively, and $UD$ is the total number of virtual resources. In addition, the second kernel of MGW has the depth of $O(1)$ and work of $O(UD)$.

Algorithm 2 presents the WiEnTM algorithm. The algorithm first exploits the MGW algorithm in Line 1 to find the matching weights and related matrices. Lines 3 to 6 are intended to find the index in the weight matrix which offers the minimum weight for subtask $v_d^u\in\mathcal{V}_d$ to obtain the corresponding optimal virtual matching. In this kernel, we consider $r_{\min}$ as a temporary variable to store the minimum-weighted virtual resource. Let $\boldsymbol{X}^{\text{virt}^{\ast}} = \left(x_{v_d^u,r_{t,v_d^u}}^{\text{virt}^{\ast}}\right)_{\left(\sum_{d\in\mathcal{D}}{\left(V_d-2\right)}\right)\times|\mathcal{R}^{\text{virt}}|}$denote the optimal virtual matching. In Line 5, we set the corresponding position in $\boldsymbol{X}^{\text{virt}^{\ast}}$ matrix. The last loop of Algorithm 2 from Line 7 to Line 15 aims to map $\boldsymbol{X}^{\text{virt}^{\ast}}$ to the corresponding optimal decision matrix which we denote as $\boldsymbol{X}^{\ast}$. In addition, we also determine the optimal values of $\boldsymbol{p}$ and $\boldsymbol{T}$ denoted as $\boldsymbol{p}^{\ast}$ and $\boldsymbol{T}^{\ast}$, respectively. This is done according to the matching graph and the output of the previous stage. We know that the non-zero element in each row of $\boldsymbol{X}^{\text{virt}^{\ast}}$ corresponds to the optimal matching of a subtask. We can obtain the optimal values of $\boldsymbol{X}^{\ast}$ and $\boldsymbol{T}^{\ast}$ by executing Line 11. In order to calculate the optimal vector of WET powers $\boldsymbol{p}^{\ast}$, we need to find the maximum value of $p_{v_d^u}^{\ast}$ over all WDs according to (\ref{eq29}) (Line 14).

We further analyze the complexity of WiEnTM algorithm. The argmin operation (Line 4) is only executed over three virtual resources of the subtask. Therefore, the depth and work of the block in Lines 3-6 are $O(1)$ and $O(UD)$, respectively. In the next kernel, finding the non-zero element in each row only requires three comparisons. As a result, the primitive in this block has the time complexity of $O(1)$. Therefore, the depth of this kernel over WDs has the complexity of $O(1)$. It also has the work with complexity $O(|\mathcal{D}^u|)=O(D)$. In Line 14, we execute a $\max$ operation. In general, maximization is a traditional reduction operation which can be parallelized in a tree-like structure with the depth of $O(\log_2D)$ and the work of $O(2D)$. Therefore, the last stage of the algorithm has the depth of $O(U\log_2D)$ and the work of $O(UD)$.

\begin{figure}
	\centering
	\begin{subfigure}{.2\textwidth}
		\centering
		\includegraphics[width=\linewidth]{tcg1.pdf}
		\caption{}
		\label{fig:5a}
	\end{subfigure}\hspace{6mm}
	\begin{subfigure}{.2\textwidth}
		\centering
		\includegraphics[width=\linewidth]{tcg2.pdf}
		\caption{}
		\label{fig:5b}
	\end{subfigure}

	\caption{Task call graph of a) WD1 and b) WD2. The numbers on each node represent the sequence in which the corresponding subtask is executed as well as the normalized computation cycle. Edge weights are input/output data sizes of subtasks in Kbits.} \label{fig:5}
\end{figure}

\begin{figure*}[ht]
	\centering
	\begin{subfigure}[b]{.22\textwidth}
		\centering
		\includegraphics[width=\linewidth]{simulation_a.pdf}
		\caption{} \label{fig:6a}
	\end{subfigure}\hspace{15mm}
	\begin{subfigure}[b]{.22\textwidth}
		\centering
		\includegraphics[width=\linewidth]{simulation_b.pdf}
		\caption{} \label{fig:6b}
	\end{subfigure}\hspace{15mm}
	\begin{subfigure}[b]{.22\textwidth}
		\centering
		\includegraphics[width=\linewidth]{simulation_c.pdf}
		\caption{} \label{fig:6c}
	\end{subfigure}

	\caption{Impact of increasing the task's total number of CPU cycles \textcolor{blue}{(i.e., $\sum_{v_d\in\mathcal{V}_d}C_{v_d}$)} on a) The optimal number of offloading decisions of WD1, b) the optimal number of offloading decisions of WD2, and c) ET's transmitted energy, for constant and adaptive $\beta_{v_d^u}$ approaches.} \label{fig:6}
\end{figure*}

As the value of $U$ represents the maximum number of subtasks among devices, it does not scale with the size of network $D$. Therefore, we can consider it as a constant in analyzing time complexity. To summarize, by considering this fact, the depth and work of our parallel WiEnTM algorithm are $O(\log_2D)$ and $O(D)$, respectively.

\section{Performance Evaluation}
In this section, we investigate the performance of WiEnTM algorithm by evaluating the computation time of tasks and the ET's energy transmission. We further compare our proposed algorithm with an existing work in \cite{b13}.

\subsection{Simulation Setup}
We consider two devices WD1 and WD2 with task call graphs shown in Fig. \ref{fig:5a} and Fig. \ref{fig:5b}. \textcolor{blue}{These figures show the dependencies in the task call graph of each WD. An arrow leaving node $i$ toward $j$ indicates that task $j$ is dependent on task $i$.} The size of subtasks to be transferred between the devices and cloud/MEC server is shown in Kbits as the weight of edges. The normalized computation cycles of each subtask is also shown next to the vertices. This value reflects the required computation cycles for each subtask \textcolor{blue}{(i.e., $C_{v_d^u}, \forall d\in\mathcal{D}^u, \forall u\in\mathcal{U}$)} divided by the task's total computation cycle \textcolor{blue}{(i.e., $\sum_{u\in\mathcal{U}}C_{v_d^u}, \forall d\in\mathcal{D}$)}. Constant parameters are set as $\zeta_1=\zeta_2=10^{-28} \text{F}$ (i.e., CPU's effective switched capacitance)\cite{b2}, $\eta_1=\eta_2=0.51$ (i.e., energy harvesting efficiency) \cite{b2}, $\sigma^2=10^{-9}\text{W}$ (i.e., noise power) \cite{b2}, $\Gamma_1=0.8\text{s}$, $\Gamma_2=\Gamma_3=\Gamma_4=\Gamma_5=0.6\text{s}$, $\Gamma_6=0.3\text{s}$, $\Gamma_7=0.4\text{s} \text{ (i.e., length of each episode)}$, $P^{\text{ET}, \max} = 50\text{W}$, $P^{\text{AP}, \max} = 25\text{W}$, and $P^{\text{WD}, \max}_1 = P^{\text{WD}, \max}_2 = 25\text{mW}$. We set the cloud response times $\mu_{v_d^u}=20\text{ms}, \forall d\in\mathcal{D}^u, \forall u\in\mathcal{U}$ as inspired by \cite{b24}. We also set $B_1 = B_2 = 50\text{MHz}, F_{1}^{\text{L},\max} = F_{2}^{\text{L},\max} = 160\text{MHz}$, and $F^{\text{M},\max} = 2.2\text{GHz}$. We adopt the simplified path loss model \cite{b21} for wireless channel gains. Without loss of generality, we set $g_d = h_d = -5\text{dB}, \forall d\in\mathcal{D}$.

In order to analyze the effect of $\beta_{v_d^u}$ on the optimal solution, we consider two cases for $\beta_{v_d^u}$ :
1) Constant with $\beta_{v_d^u}=1, \forall v_d^u\in \mathcal{V}_d$, 2) adaptive $\beta_{v_d^u}$ with $0\leq k \leq 1$ given as follows.
\begin{equation}\label{eq32}
	\begin{aligned}
		\beta_{v_d^u} = &\frac{kC_{v_d^u}}{\sum_{d'\in\mathcal{D}^u}C_{v_{d'}^u}}|\mathcal{D}^u| +\\
		&\frac{(1-k)\sum_{v_d^i\in\mathcal{I}_{v_{d'}^u}}N_{v_{d'}^i,v_d^u}}{\sum_{d'\in\mathcal{D}^u}\sum_{v_{d'}^i\in\mathcal{I}_{v_{d'}^u}}N_{v_{d'}^i,v_{d'}^u}}|\mathcal{D}^u|,\quad\forall d\in\mathcal{D}^u, \forall u\in\mathcal{U},
	\end{aligned}
\end{equation}
where we consider $k=0.8$. Note that the above value is an example of adaptive $\beta_{v_d^u}$ and determining it's optimal value is beyond the scope of this work. \footnote{\textcolor{blue}{For the case of non-optimal $\beta_{v_d^u}$, one needs to analyze the approximation ratio of the proposed algorithm. An approach similar to \cite{b2} can be followed. However, we leave this extension as future work.}}

\begin{figure}
	\centering
	\begin{subfigure}[b]{.39\textwidth}
		\centering
		\includegraphics[width=\linewidth]{simulation2_a1.pdf}
		\caption{} \label{fig:7a1}
	\end{subfigure}
	\begin{subfigure}[b]{.39\textwidth}
		\centering
		\includegraphics[width=\linewidth]{simulation2_b1.pdf}
		\caption{} \label{fig:7b1}
	\end{subfigure}

	\caption{The total computation time of our three-tier WPMEC and the scheme proposed in \cite{b13} for different task's total CPU cycles \textcolor{blue}{(i.e., $\sum_{v_d\in\mathcal{V}_d}C_{v_d}$)} for a) WD1, and b) WD2.} \label{fig:71}
\end{figure}

We now describe the intuition behind the adaptive $\beta_{v_d^u}$ value given in (\ref{eq32}). According to (\ref{eq2}) and (\ref{eq3}), it can be observed that increasing the number of CPU cycles and input/output data bits of each subtask will increase the energy required by the subtask. Constraint (\ref{eq28}) depicts that increasing $\beta_{v_d^u}$ will expand the feasible space for $\tau_{1,v_d^u}$ and $\tau_{2,v_d^u}$ which will decrease the energy consumption. Therefore, subtasks with high number of CPU cycles and high amount of input/output data bits are the bottleneck of energy consumption. As a result, modeling $\beta_{v_d^u}$ based on a weighted sum of normalized number of CPU cycles and input/output bits should decrease the energy consumption compared to assigning equal $\beta_{v_d^u}$ to all subtasks.

\begin{figure}
	\centering
	\begin{subfigure}[b]{.37\textwidth}
		\centering
		\includegraphics[width=\linewidth]{simulation2_a.pdf}
		\caption{} \label{fig:7a}
	\end{subfigure}
	\begin{subfigure}[b]{.37\textwidth}
		\centering
		\includegraphics[width=\linewidth]{simulation2_b.pdf}
		\caption{} \label{fig:7b}
	\end{subfigure}

	\caption{\textcolor{blue}{Comparison of ET's transmitted energy between WiEnTM and the algorithm proposed in \cite{b13} for different a) task's CPU cycles (i.e., $\sum_{v_d\in\mathcal{V}_d}C_{v_d}$) and, b) task's internal input/output bits (i.e., $\sum_{v_d^i,v_d^j\in\mathcal{V}_d}N_{v_d^i,v_d^j}$).}} \label{fig:7}
\end{figure}

\subsection{Simulation Results}
Figs. \ref{fig:6a} and \ref{fig:6b} show the transition between different optimal offloading decisions as we increase the task's CPU cycles \textcolor{blue}{(i.e., $\sum_{u\in\mathcal{U}}C_{v_d^u}, \forall d\in\mathcal{D}$)} for WD1 and WD2, respectively. In both of these figures, we illustrate the number of offloading decisions for the local, edge, and cloud computing. Note that for each WD, the sum of offloading decisions is the number of subtasks. It can be observed that as we increase the task CPU cycles, the offloading decisions gradually transit from the local to the edge and finally to the cloud. Additionally, it is shown that for WD1 which has a larger number of task CPU cycles, the system relies more on the cloud server than WD2. Fig. \ref{fig:6c} shows the  optimal ET’s energy transmission. From Fig. \ref{fig:6c}, it can be perceived that adaptive technique offers up to 47\% less energy consumption in comparison with the constant $\beta_{v_d^u}$ approach. It means that setting $\beta_{v_d^u}$ according to the number of CPU cycles and input/output sizes greatly enhances the performance comparing to the constant approach.

By considering adaptive $\beta_{v_d^u}$ given in (\ref{eq32}), we also compare our proposed three-tier WPMEC system with the scheme proposed in \cite{b13}. Figs. \ref{fig:7a1} and \ref{fig:7b1} illustrate the task's execution time for WD1 and WD2, respectively. The results show that by using WiEnTM, up to $13\%$ overall less total computation time can be obtained for WD1 in comparison to \cite{b13}. This is because WD1 has a computationally intensive task. However, a lower improvement is achieved for WD2 as it has a lighter task which is mostly executed locally by the device or on the MEC server.

\textcolor{blue}{We further investigate the performance of our proposed WiEnTM algorithm by evaluating the ET's transmitted energy in comparison to that of \cite{b13}. Figs. \ref{fig:7a} and \ref{fig:7b} illustrate the effect of the task's CPU cycles and the task size (i.e., the number of input/output bits), respectively. The results show that by using WiEnTM, the ET consumes up to $34\%$ less energy compared to the algorithm in \cite{b13}.}

\textcolor{blue}{We now consider 200 WDs and investigate the ET transmission energy required to enable WDs execute their tasks. We study three different policies: 1) Local computing, 3) computation offloading, and 3) WiEnTM algorithm. We assume that among these devices, 100 WDs have a task with the call graph shown in Fig. \ref{fig:5a} and the rest with the task call graph of Fig. \ref{fig:5b}.} In the local computing case, all WDs harvest the energy to execute their subtasks locally while in the computation offloading case, the energy is used to offload all the subtasks. \textcolor{blue}{Fig. \ref{fig:9a} shows the ET's energy transmission when we vary the task's total CPU cycles. Additionally, Fig. \ref{fig:9b} illustrates the ET's energy for different numbers of the task's total input/output bits, which reflect the size of the tasks.} As can be observed, WiEnTM substantially reduces the required energy as it achieves the optimal offloading decisions. \textcolor{blue}{In particular, according to Fig. \ref{fig:9a}, comparing to the local computing case, a higher improvement is obtained for the computationally intensive tasks.} This is because the WDs require more energy to execute all their subtasks locally. However, for light tasks with low computation cycles, the WiEnTM algorithm significantly outperforms the offloading case as it is more preferred to execute such tasks locally. \textcolor{blue}{The results of Fig. \ref{fig:9b} imply that WiEnTM mainly follows the policy of offloading to edge/cloud server for tasks with a small number of input/output bits. As we increase the number of bits, the algorithm tends to rely more on local computing. As can be observed, WiEnTM greatly outperforms both schemes.}

\begin{figure}
	\centering
	\begin{subfigure}[b]{.24\textwidth}
		\centering
		\includegraphics[height=1.2\linewidth]{simulation3_a.pdf}
		\caption{} \label{fig:9a}
	\end{subfigure}
	\begin{subfigure}[b]{.24\textwidth}
		\centering
		\includegraphics[height=1.2\linewidth]{simulation3_b.pdf}
		\caption{} \label{fig:9b}
	\end{subfigure}

	\caption{\textcolor{blue}{Comparison of ET's transmitted energy for three offloading policies when there are 200 WDs. 1) Local computation-only, 2) computation offloading-only, and 3) WiEnTM algorithm.}} \label{fig:9}
\end{figure}
